Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-06-04 ms.tex
adding TODO for beginning of Comparison to Monte Carlo subsection

We now compare each of these solutions for surface flux with Monte Carlo simulations for a limited range of physical parameters $\tau_0$ and $x_s$. In Fig. \ref{fig:sol_mc_residual_0}, the Monte Carlo is shown with solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ overplotted for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\sigma_s = \sigma_0$. The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing. It is evident that the divergent solution $H_{\rm d}$ fails in the line wings. The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum. This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S}. The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, improving agreement with the numerical result.

>>>>

\todo{Brief description of MC code, citing Chenliang's paper. Discuss how MC works briefly, reference some papers, talk about problem setup specific to this work. Basically want to show that the MC approach in this paper is not new and doesn't need to be justified extensively.}

We now compare each of these solutions for surface flux with Monte Carlo simulations for a limited range of physical parameters $\tau_0$ and $x_s$. In Fig. \ref{fig:sol_mc_residual_0}, the Monte Carlo is shown with solutions $H_{\rm d}$, $H_{\rm 0}$, and $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$ overplotted for an optical depth of $\tau_0 = 10^7$ and photons emitted at line center $\sigma_s = \sigma_0$. The solution with the correct frequency-dependent boundary condition enforced, $H_{\rm 0 + bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing. It is evident that the divergent solution $H_{\rm d}$ fails in the line wings. The $H_{\rm bc}$ term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, adequately corrects for the apparent excess of flux in the peaks of the spectrum. This peak excess is also present in previous work that used the \citet{1990ApJ...350..216N} solution, such as \citet{2015MNRAS.449.4336S}. The boundary term resolves the slight deficit of $H_{\rm0}$ in the line wings, further improving agreement with the numerical result.
